A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-16 pilot-publication/manuscript.Rmd
Remove new lines and add comparison of observed and extracted data

We also assessed the following feasibility outcomes, which pertain
both to overall study population as well as to the individual cluster
level:

@@

## Patient and public involvement
In this study, we conducted community consultations to collect
inputs from patients, their caregivers, patient groups, and resident
doctors to be used in the selection of outcome measures and
implementation of the full-scale trial; following the Guidance for
Reporting Involvement of Patients and the Public (GRIIPS 2)
[@Staniszewska2017]. The results of these consultations will be reported 
separately.

@@

## Statistical Methods
We analysed all pilot data using descriptive statistics. Quantitative
variables are summarised as mean +/- standard deviation, median,
interquartile range and range. Qualitative variables are presented as
absolute numbers and percentages. Feasibility outcomes are summarised
both on the overall sample level as well as on the individual cluster
level. We used an empty generalised linear mixed model<!-- see
[@Sommet2017] --> to estimate the intracluster correlation
coefficient.

@@

## Resident Participant Outcomes
A total of `r n.residents` residents were trained during this
pilot. Overall their median confidence in managing trauma patients was `r median.confidence` (IQR `r iqr.confidence`) on a 10 point Likert scale with 10 being most confident. <!--In the post training period, the confidence in the ATLS arm was X (IQR X - X), compared to X (IQR X - X) in the PTC arm, and X (IQR X - X) in the standard care arm.-->

## Feasibility Outcomes
<!--Out of X potentially eligible patients, X (X%) patients were enrolled
in the study-->. Out of `r n.eligible.residents` potentially eligible residents, `r n.residents` (`r recruitment.rate.residents`%) participated in the study. The lost to follow up rate was `r rate.lost.to.follow.up`, with `r n.lost.to.follow.up` out of `r n.patients` patients not completing 30 day follow up. Among residents the pass rate, after two attempts, was `r rate.pass`%. The missing data rate ranged from `r min.missing.data` to `r max.missing.data`, with details per variable and outcome in Table  \ref@(tab:sample-characteristics) and Supplementary material table
\@ref(tab:secondary-outcomes). <!--The differences in distributions between observed and extracted data, for variables that were collected through observation or interview, are shown in Table X.-->

## Community Consultations
The results of interviews with patients, caregivers and social workers
will be published separately. Residents felt that...

>>>>

We also assessed the following feasibility outcomes, which pertained both to overall study population as well as to the individual cluster level:

@@

## Patient and public involvement
In this study, we conducted community consultations to collect
inputs from patients, their caregivers, patient groups, and resident doctors to be used in the selection of outcome measures and implementation of the full-scale trial; following the Guidance for Reporting Involvement of Patients and the Public (GRIIPS 2) [@Staniszewska2017]. The results of these consultations will be reported in a separate publication.

@@

## Statistical Methods
We analysed all pilot data using descriptive statistics. Quantitative variables are summarised as mean +/- standard deviation, median, interquartile range and range. Qualitative variables are presented as absolute numbers and percentages. Feasibility outcomes are summarised both on the overall sample level as well as on the individual cluster level. We used an empty generalised linear mixed model <!-- see [@Sommet2017] --> to estimate the intracluster correlation coefficient.

@@

## Resident Participant Outcomes
A total of `r n.residents` residents were trained during this
pilot study. Overall their median confidence in managing trauma patients was `r median.confidence` (IQR `r iqr.confidence`) on a 10 point Likert scale with 10 being most confident. <!--In the post training period, the confidence in the ATLS arm was X (IQR X - X), compared to X (IQR X - X) in the PTC arm, and X (IQR X - X) in the standard care arm.-->

## Feasibility Outcomes
<!--Out of X potentially eligible patients, X (X%) patients were enrolled
in the study-->. Out of `r n.eligible.residents` potentially eligible residents, `r n.residents` (`r recruitment.rate.residents`%) participated in the study. The lost to follow up rate was `r rate.lost.to.follow.up`, with `r n.lost.to.follow.up` out of `r n.patients` patients not completing 30 day follow up. Among residents the pass rate, after two attempts, was `r rate.pass`%. The missing data rate ranged from `r min.missing.data` to `r max.missing.data`, with details per variable and outcome in Table  \ref@(tab:sample-characteristics) and Supplementary material table
\@ref(tab:secondary-outcomes). The differences in distributions between observed and extracted data, for selected variables that were collected through observation or interview, are shown in Table \ref@(tab:observed-vs-retrospective). Overall, there were considerably more missing values in extracted data compared to observed data.

```{r observed-vs-retrospective, echo = FALSE}
retrospective.comparison.table %>%
  modify_caption("Differences in distributions between observed and extracted data, for selected variables that were collected through observation or interview.")
```
